---
title: "A Simple Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simple-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set directories and install libraries

```{r eval = FALSE}

#get rid of memory limits
options(future.globals.maxSize = 1 * 1024^4)  # Allow up to 1 TB for globals

# Set directories --------------------------------------------------------------
library(here)

wd <- paste0(here::here(),"/vignettes/")
dir_out <- paste0(wd, "output/")
crs_latlon <- "+proj=longlat +datum=WGS84" # decimal degrees

# Install Libraries ------------------------------------------------------------

# Here we list all the packages we will need for this whole process
# We'll also use this in our works cited page. 
PKG <- c(
  "surveyresamplr",
  
  # tidyverse
  "dplyr",
  "magrittr",
  "tidyr",
  "viridis",
  "ggplot2", 
  "tibble",
  "janitor", 
  "data.table", 
  
  # parallelizing
  "forcats",
  "purrr",
  "furrr", 
  "doParallel",
  
  # sampling
  "sampling",
  
  # modeling
  "arrow", 
  "future.apply", 
  "future.callr", 
  "sdmTMB", # install.packages("remotes"",; remotes::install_github("pbs-assess/sdmTMBextra", dependencies = TRUE",
  "Matrix", 
  "MASS",
  "cluster", 
  "TMB", 
  "INLA" 
)

pkg_install <- function(p){
  if(!require(p, character.only = TRUE)) {
    install.packages(p)
  }
  require(p, character.only = TRUE)
}
base::lapply(unique(PKG), pkg_install)
```

## Test Species List

Then we define our species and model list. In this simple example, we'll assess a model for eastern Bering Sea (EBS) walleye pollock (*Gadus chalcogrammus*) from 2010-present, using data collected by the Alaska Fisheries Science Center. 

Walleye pollock are fairly well distributed across the area, very common in the area, and very economically important, so this will be a great species to start testing these models with. 

```{r define-spp-list}
spp_list <- data.frame(
  srvy = "EBS",
  common_name = c("walleye pollock"), 
  species_code = as.character(c(21740)),
  filter_lat_lt = NA, 
  filter_lat_gt = NA, 
  filter_depth = NA, 
  model_fn = "total_catch_wt_kg ~ 0 + factor(year)",
  model_family = "delta_gamma",
  model_anisotropy = TRUE,
  model_spatiotemporal = c(c("iid, iid"))
) %>% 
  dplyr::mutate( 
    file_name = gsub(pattern = " ", replacement = "_", x = (tolower(common_name)))  )
```

## Pull in data

Some example data is included in the R package for examples like this. We'll need 

1. Zero-filled catch data from the survey to use for developing the model and 
2. an extrapolation grid that you can replicate across years for your prediction matrix. Note that if your model models over depth (as with this model) your prediction grid will also need to have a depth field. 

Use `?surveyresamplr::noaa_afsc_catch` and `?surveyresamplr::noaa_afsc_ebs_pred_grid_depth`) to learn more about these data sources. In the meantime, this is what these resources look like: 

```{r explore-catch}
# ?surveyresamplr::noaa_afsc_catch

head(surveyresamplr::noaa_afsc_catch)

# Example exploratory plot

dat <- surveyresamplr::noaa_afsc_catch %>% 
                  dplyr::filter(year %in% 2023:2024 & 
                                  srvy %in% c("EBS") & 
                                  species_code == 21740)

ggplot2::ggplot(data = dat %>% dplyr::filter(cpue_kgkm2 != 0), 
                mapping = aes(x = longitude_dd, 
                              y = latitude_dd, 
                              size = cpue_kgkm2)) + 
  ggplot2::geom_point(alpha = .75) +
  ggplot2::geom_point(data = dat %>% dplyr::filter(cpue_kgkm2 %in% c(0, NA)), 
                      color = "red", 
                      shape = 17,
                      alpha = .75,
                      size = 3) +
  ggplot2::xlab("Longitude *W") +
  ggplot2::ylab("Latitude *N") +
  ggplot2::ggtitle(label = "CPUE (kg/km^2) of walleye pollock (Weight CPUE; kg/km2)", 
                   subtitle = "AFSC Eastern Bering Sea bottom trawl survey") +
  ggplot2::scale_size_continuous(name = "Weight (kg)") + 
  ggplot2::facet_wrap(facets = vars(year)) + 
  ggplot2::theme_bw()
```


```{r explore-grid}
# ?surveyresamplr::noaa_afsc_ebs_pred_grid_depth

head(surveyresamplr::noaa_afsc_ebs_pred_grid_depth)

ggplot2::ggplot(data = surveyresamplr::noaa_afsc_ebs_pred_grid_depth, 
       mapping = aes(x = longitude_dd, 
                     y = dat$latitude_dd, 
                     color = dat$depth_m)) + 
  ggplot2::geom_point(alpha = .5, 
                      size = .5)  +
  ggplot2::xlab("Longitude *W") +
  ggplot2::ylab("Latitude *N") +
  ggplot2::ggtitle(label = "Prediction Grid", 
                   subtitle = "AFSC Eastern Bering Sea bottom trawl survey") +
  ggplot2::scale_color_continuous(name = "Depth (m)") + 
  ggplot2::theme_bw() + 
  
```   


Here we load the data for the model run, cropping it to the data we would like to include (the EBS survey and years greater than 2010) and replicating the the prediction grid across the years in the catch data. 

```{r load-data}
### Load survey data -----------------------------------------------------------

catch <- surveyresamplr::noaa_afsc_catch %>% 
  dplyr::filter(srvy == "EBS") %>% 
  dplyr::filter(year > 2010)

### Load grid data -------------------------------------------------------------

grid_yrs <- replicate_df(dat = surveyresamplr::noaa_afsc_ebs_pred_grid_depth, 
                         time_name = "year", 
                         time_values = unique(catch$year))

### Variables ------------------------------------------------------------------

srvy <- "EBS"
seq_from = 0.2
seq_to = 1.0
seq_by = 0.2 
tot_dataframes = 13
replicate_num <- 3

### Run ------------------------------------------------------------------------

sink(file = paste0(dir_out, srvy, "_", Sys.Date(), "_logfile.txt"), append=FALSE, split=TRUE)  # for screen and log
map(
  1:nrow(spp_list), 
  ~ clean_and_resample(spp_list[.x,], 
                       catch, seq_from, seq_to, seq_by, 
                       tot_dataframes, replicate_num, grid_yrs, dir_out))
sink()

### Plot indices ---------------------------------------------------------------

aaa <- plot_results(srvy = srvy, dir_out = dir_out) 

aaa
```
